---
title: "Rmd for CCM Coding Camp"
author: "Linda"
date: "11 12 2017"
output: beamer_presentation
---

# Start

This is the start of the introductory Rmd File for the CCM Coding Camp 2017. It will take place on Monday, Dec `r 5 + 6`.

```{r packages, include=FALSE}
library(ggplot2)
library(knitr)
```

# Code Chunks

```{r}
str(mtcars[1:2,1:2])
```

# Knits options

Set global knitr options with the following code chunk:

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

Now we play around with knitr options:

* The code chunk is not shown but results can be used with include.

```{r, include = FALSE}
a = data.frame(mpg = mtcars$mpg)
```

* Now use the just assigned variable a where the reader does not know where it comes from.

```{r}
ggplot(a, aes(x = mpg)) +
    geom_histogram()
```

* The message is annoying so we can get rid of it:

```{r, message=FALSE, echo = FALSE}
ggplot(a, aes(x = mpg)) +
    geom_histogram()
```

# Bash

```{bash}
ls -l
```

# Tables

Beautiful tables in R

```{r, results = 'asis'}
kable(mtcars[1:5, 1:3 ], caption = "A knitr kable.")
```

# Text formatting

Some (useful) text formatting: We can create lists

- *italic*
- **bold**
- `code`
- Latex equations: $a^2 + b^2 = c^2$


